---
output:
  md_document:
    variant: markdown_github
---

# 22568948 Data Science Practical Exam

In this markdown folder I will explain my thinking and working for the coding aspect of the Data Science Methods for Economics and Finance final exam in June 2024. I will work through the questions one by one and talk through the code that I wrote to complete it.


```{r, results='hide', message=FALSE, warning=FALSE}

rm(list = ls()) # Clean your environment:
gc()
setwd("C:/Users/andre/OneDrive/Documents/Masters_2024_stuff/Data_Science/Data_Science_Exam/22568948")

library(tidyverse)
```

##Question 1

It is firstly important that the working directory of the project is properly allocated as the directory is used to create folders and projects.  

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly I create the Texevier project for writing the report and coding in Question 1
#Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_1")

#Secondly I fetch the functions that I wrote from the code folder in Question 1
list.files('Question_1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

```

The first command that is run is to create a Texevier HTML project under the title Question_1 wherein I complete the question. The second is to fetch the functions that I create while writing the report for question 1.

```{r, results='hide', message=FALSE, warning=FALSE}
Baby_names_df <- Data_Reading("Question_1/data/Baby_Names_By_US_State.rds")
```

This function simply read the data from the given rds file into a dataframe that can be used in the report. No data transformations take place in this function.

```{r, message=FALSE, warning=FALSE}
plot_corr <- Corr_plot(Baby_names_df)
plot_corr
```

This function transforms the base dataframe to a format that can be used to plot the Spearman correlation over time. The first step is to rank the most popular names from each year across the United States. This is done by grouping by year and name and them summarising to get to get the totals. Then we arrange the totals in descending order according to the totals of each name in each year. We can then rank by group to get the ranking in each year.

Once we have this we can rename the rank variable and mutate the year to be _no_Years_ years earlier (where _no_Years_ can be set, default is 3). We can then left_join the dataframe with the renamed and mutated dataframe to get the rank of the names in the start year and the later year. We then arrange by the rank in the start year and use "slice_head" to get the top _no_top_ names per year (where _no_top_ can be set, the default is 25). Correlation is then calculated between the ranks of the names in the start year and their rank x years later, the Spearman method is used.

This is then plotted using a geometric line graph to show the changes in correlation over time, geometric points are added to highlight the exact points in time and finally a geom_smooth plot is used to show a smoothed mean across time with a confidence interval of _conf_level_ (where _conf_level_ can be set, the default is 0.95).

```{r, message=FALSE, warning=FALSE}
plot_ridge <- Ridge_plot(Baby_names_df)
plot_ridge
```

This first step in this function is to take the same base dataframe and group by name and summarise by count to get the total count of babies per baby name. Using arrange and head we can get the top _no_names_ most used names (where _no_names_ can be set, default is 15). 

Then I can group by Year and Name to summarise by count and filter for the top _no_names_ names in each year. I then use the ggridges package to plot a density ridge plot for the popularity of the most popular names over time. Using alpha = 0.5 to make the graphs more see through. 

##Question 2

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
#Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_2")


```

##Question 3

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
#Texevier::create_template(directory = glue::glue("{getwd()}/"), template_name = "Question_3_1")


```

##Question 4

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
#Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_4")


```

##Question 5

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
#Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_5")

```


