---
output:
  md_document:
    variant: markdown_github
---

#22568948 Data Science Practical Exam

The purpose of this README markdown file is to explain my thinking during the coding aspect of the final exam for Data Science Methods for Economics and Finance in June 2024.


```{r, results='hide', message=FALSE, warning=FALSE}

rm(list = ls()) # Clean your environment:
gc()
setwd("C:/Users/andre/OneDrive/Documents/Masters_2024_stuff/Data_Science/Data_Science_Exam/22568948")

library(tidyverse)

list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

##Question 1

It is firstly important that the working directory of the project is properly allocated as the directory is used to create folders and projects.

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly I create the Texevier project for writing the report and coding in Question 1
Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_1")

#Secondly I fetch the functions that I wrote from the code folder in Question 1
list.files('Question_1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))


```

\newpage

##Question 2

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_2")


```

##Question 3

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_3")


```

##Question 4

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_4")


```

##Question 5

```{r, results='hide', message=FALSE, warning=FALSE}
#Firstly Create the Texevier project
Texevier::create_template_html(directory = glue::glue("{getwd()}/"), template_name = "Question_5")

```


